% منابع فصل دوم؛ در انتهای فایل اصلی و پس از \backmatter درج شود.
\begin{thebibliography}{99}
\begin{LTR}

\bibitem{shannon1949communication}
C. E. Shannon,
``Communication in the Presence of Noise,''
\emph{Proceedings of the IRE}, vol. 37, no. 1, pp. 10--21, 1949.

\bibitem{unser2000sampling}
M. Unser,
``Sampling---50 Years after Shannon,''
\emph{Proceedings of the IEEE}, vol. 88, no. 4, pp. 569--587, 2000.

\bibitem{papoulis1977generalized}
A. Papoulis,
``Generalized Sampling Expansion,''
\emph{IEEE Transactions on Circuits and Systems}, vol. 24, no. 11, pp. 652--654, 1977.

\bibitem{unser2000generalized}
M. Unser and A. Aldroubi,
``A General Sampling Theory for Nonideal Acquisition Devices,''
\emph{IEEE Transactions on Signal Processing}, vol. 42, no. 11, pp. 2915--2925, 1994.

\bibitem{unser1999splines}
M. Unser,
``Splines: A Perfect Fit for Signal and Image Processing,''
\emph{IEEE Signal Processing Magazine}, vol. 16, no. 6, pp. 22--38, 1999.

\bibitem{gonzalez2018dip}
R. C. Gonzalez and R. E. Woods,
\emph{Digital Image Processing}, 4th ed., Pearson, 2018.

\bibitem{oppenheim1999dsp}
A. V. Oppenheim, R. W. Schafer, and J. R. Buck,
\emph{Discrete-Time Signal Processing}, 2nd ed., Prentice Hall, 1999.

\bibitem{max1960quantizing}
J. Max,
``Quantizing for Minimum Distortion,''
\emph{IRE Transactions on Information Theory}, vol. 6, no. 1, pp. 7--12, 1960.

\bibitem{lloyd1982least}
S. P. Lloyd,
``Least Squares Quantization in PCM,''
\emph{IEEE Transactions on Information Theory}, vol. 28, no. 2, pp. 129--137, 1982.

\bibitem{lbg1980vq}
Y. Linde, A. Buzo, and R. M. Gray,
``An Algorithm for Vector Quantizer Design,''
\emph{IEEE Transactions on Communications}, vol. 28, no. 1, pp. 84--95, 1980.

\bibitem{gray1998quantization}
R. M. Gray and D. L. Neuhoff,
``Quantization,''
\emph{IEEE Transactions on Information Theory}, vol. 44, no. 6, pp. 2325--2383, 1998.

\bibitem{emva1288r4}
European Machine Vision Association,
\emph{EMVA Standard 1288, Release 4.0: Standard for Characterization of Image Sensors and Cameras}, 2021.

\bibitem{janesick2007photon}
J. R. Janesick,
\emph{Photon Transfer: DN $\to$ $\lambda$}, SPIE Press, 2007.

\bibitem{bayer1976patent}
B. E. Bayer,
``Color Imaging Array,'' U.S. Patent 3,971,065, 1976.

\bibitem{malvar2004demosaic}
H. S. Malvar, L. He, and R. Cutler,
``High-Quality Linear Interpolation for Demosaicing of Bayer-Patterned Color Images,''
\emph{Proceedings of ICASSP}, vol. 3, pp. 485--488, 2004.

\bibitem{brooks2019unprocessing}
T. Brooks, B. Mildenhall, T. Xue, J. Chen, D. Sharlet, and J. T. Barron,
``Unprocessing Images for Learned Raw Denoising,''
\emph{CVPR}, pp. 11036--11045, 2019.

\bibitem{ehret2019joint}
T. Ehret, A. Davy, P. Arias, and G. Facciolo,
``Joint Demosaicking and Denoising by Fine-Tuning of Bursts of Raw Images,''
\emph{ICCV}, pp. 8868--8877, 2019.

\bibitem{grossberg2003crf}
M. D. Grossberg and S. K. Nayar,
``What Is the Space of Camera Response Functions?''
\emph{CVPR}, vol. 2, pp. II-602--II-609, 2003.

\bibitem{debevec1997hdr}
P. E. Debevec and J. Malik,
``Recovering High Dynamic Range Radiance Maps from Photographs,''
\emph{Proceedings of SIGGRAPH}, pp. 369--378, 1997.

\bibitem{mitsunaga1999radiometric}
T. Mitsunaga and S. K. Nayar,
``Radiometric Self Calibration,''
\emph{CVPR}, vol. 1, pp. 374--380, 1999.

\bibitem{cie2019observer}
CIE,
\emph{ISO/CIE 11664-1:2019, Colorimetry---Part 1: CIE Standard Colorimetric Observers}, 2019.

\bibitem{cie2018colorimetry}
CIE,
\emph{CIE 15:2018, Colorimetry}, 4th ed., 2018.

\bibitem{iec61966srgb}
IEC,
\emph{IEC 61966-2-1:1999, Multimedia Systems and Equipment---Colour Measurement and Management---Part 2-1: Default RGB Colour Space---sRGB}, 1999.

\bibitem{iturbt709}
ITU-R,
\emph{Recommendation BT.709-6: Parameter Values for the HDTV Standards for Production and International Programme Exchange}, 2015.

\bibitem{iturbt2020}
ITU-R,
\emph{Recommendation BT.2020-2: Parameter Values for Ultra-High Definition Television Systems for Production and International Programme Exchange}, 2015.

\bibitem{iturbt2100_3}
ITU-R,
\emph{Recommendation BT.2100-3: Image Parameter Values for High Dynamic Range Television for Use in Production and International Programme Exchange}, Feb. 2025.

\bibitem{zhang2019shift}
R. Zhang,
``Making Convolutional Networks Shift-Invariant Again,''
\emph{Proceedings of the 36th International Conference on Machine Learning},
PMLR 97, pp. 7324--7334, 2019.

\bibitem{karras2021stylegan3}
T. Karras et al.,
``Alias-Free Generative Adversarial Networks,''
\emph{Advances in Neural Information Processing Systems}, vol. 34, pp. 852--863, 2021.

\bibitem{zhou2025afldm}
Y. Zhou, Z. Xiao, S. Yang, and X. Pan,
``Alias-Free Latent Diffusion Models: Improving Fractional Shift Equivariance of Diffusion Latent Space,''
\emph{CVPR}, pp. 34--44, 2025.

\bibitem{parmar2022aliased}
G. Parmar, R. Zhang, and J.-Y. Zhu,
``On Aliased Resizing and Surprising Subtleties in GAN Evaluation,''
\emph{CVPR}, pp. 11410--11420, 2022.

\bibitem{arad2022ntire}
B. Arad et al.,
``NTIRE 2022 Spectral Recovery Challenge and Data Set,''
\emph{CVPR Workshops}, pp. 863--881, 2022.

\bibitem{cai2022mst}
Y. Cai, J. Lin, Z. Lin, H. Wang, Y. Zhang, H. Pfister, R. Timofte, and L. Van Gool,
``MST++: Multi-Stage Spectral-Wise Transformer for Efficient Spectral Reconstruction,''
\emph{CVPR Workshops}, pp. 745--755, 2022.

\bibitem{zhang2022survey}
J. Zhang, R. Su, W. Ren, Q. Fu, F. Heide, and Y. Nie,
``A Survey on Computational Spectral Reconstruction Methods from RGB to Hyperspectral Imaging,''
\emph{Scientific Reports}, vol. 12, article 11905, 2022.

\bibitem{szeliski2022cv}
R. Szeliski,
\emph{Computer Vision: Algorithms and Applications}, 2nd ed., Springer, 2022.

\bibitem{reinhard2010color}
E. Reinhard, E. A. Khan, A. O. Akyüz, and G. M. Johnson,
\emph{Color Imaging: Fundamentals and Applications}, A K Peters/CRC Press, 2008.

\bibitem{fairchild2013appearance}
M. D. Fairchild,
\emph{Color Appearance Models}, 3rd ed., Wiley, 2013.

\end{LTR}
\end{thebibliography}
